\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-14 paper/main.tex
conclusion half way

We present \tname, a database of curated reproducible bugs to
enable credible evaluation of DL library testing techniques. \tname\ is
equipped with a command-line interface to enable researchers to analyze
and reproduce bug instances. The following screencast demonstrate some
of the features in \tname:

@@

\tname\ has been under active development since March 21, 2024, the
day of the first commit in the corresponding GitHub repository. Two
UROP students, two PhD students, and two faculty were involved in the
work. \tname\ is publicly available from the following URL:

@@

\begin{table}
  \centering
  \caption{\label{table:bug-characterization}Characterization of
    reproducible bugs from \tname.\Fix{Is this up to date? I have seen
  lots of activity recently but these numbers remain the
  same - Fixed (Abid)}\Fix{Can we add info about whether Python and/or C code causes
      the bug? - Abid: we report how many c,python and cuda native files are buggy in total but not per bug, so currently no}\Fix{Can we add info on whether it is GPU related
      (i.e., only manifests in GPUs)? - Abid: venv-docker is the same as cpu-gpu}}
\begin{tabular}{l|rrr}
  \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
  \\ \cmidrule(lr){2-4} \jax{} & 46 & 45-1 & 45-1 \\ \torch{} & 37 &
  18-19 & 21-16 \\ \tf{} & 24 & 23-1 & 24-0 \\ \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 86-21& 90-17
  \\ \bottomrule
\end{tabular}
\end{table}

@@

@@

\subsection{Usage}

@@

The second step runs the \tname's command \CodeIn{run-tool}, which
proceeds in two steps (1) reproduce the bug separately, as done with
command \CodeIn{run-test}, and (2) then update the environment inside
the docker container of the tool to run the tool with the script
provided.\Fix{is the container destroyed after that? you are changing
  the environment for a certain bug, right?! - Abid: the dependencies are installed inside the docker, but after running the dependencies are not reverted back. if another bug is to be reproduced, installing the new dependencies will simply overwrite the previous dependencies} The first step is a
sanity check to assure that the bug can indeed be reproduced. For
example, the following command runs FreeFuzz on the enviroment of the
bug associated with the issue 117033 from \torch.

@@

\begin{lstlisting}[language=bash]
  ...
  [Reproducing the bug]
  ====== test session starts ======
  platform linux -- Python 3.10.0, pytest-8.3.3, pluggy-1.5.0
  ...
  IndexError: list index out of range
  ====== 1 passed in 1.09s ======
  ...
  [Setting up FreeFuzz]
  Updating environment in the container of the testing tool
  Successfully copied 16.4kB to freefuzz:/tmp/issue_117033
  __pycache__  install_environment.sh  reproduce_bug.sh  requirements.txt  test_issue_117033.py
  ...
  [Running FreeFuzz]
  Running the testing tool on the environment of the bug
  Testing on  ['torch']
  torch.log2
  ...
  torch.nn.MaxUnpool2d
  ../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [1,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
  ../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [2,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
  ...
\end{lstlisting}

@@

\Fix{Please review and revise}

@@

\Fix{@Saikat, can you please write 1-2 sentences about each use case here?}

\subsection{Evaluating DL library testing techniques}
\subsection{Fault Detection}
\subsection{Program Repair}

\section{Related Work} 
Several bug datasets have been proposed in literature for general software. Some
popular examples includes software-artifact infrastructure repository
(SIR)~\cite{do2005supporting} which was one of the bug datasets containing 81
artificial faults in projects across multiple languages,
Defects4J~\cite{just2014defects4j} which includes 357 real bugs across five
large real-world Java projects, BugsInPy~\cite{widyasari2020bugsinpy} containing
493 real bugs from 17 real-world Python programs, and
BugsJS~\cite{vancsics2020relationship} containing 453 bugs across 10 Javascript
projects.
%
Google's FuzzBench~\cite{metzman2021fuzzbench} provides an evaluation platform
for comparing general purpose fuzzers. Magma~\cite{hazimeh2020magma} is another
fuzzing benchmark built by \emph{front-porting} real bugs in latest version of
projects. In contrast to these general purpose benchmarks, \tname includes
reproducible bugs for Deep Learning libraries like PyTorch and TensorFlow, and
allows systematic benchmarking for DLL fuzzers.

@@

\section{Conclusion and Future Work}

\Fix{Marcelo will write a paragraph}

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

@@

\Fix{}

>>>>

We present \tname, a database of curated reproducible bugs to
enable credible evaluation of DL library testing techniques. \tname\ is
equipped with a command-line interface to enable researchers to analyze
and reproduce bug instances. The following screencast demonstrates some
of the features of \tname:

@@

\tname\ has been under active development since March 21, 2024, the
day of the first commit in its GitHub repository. Two UROP students,
two PhD students, and two faculty were involved in the work during
this period. \tname\ is publicly available from the following URL:

@@

\begin{table}
  \centering
  \caption{\label{table:bug-characterization}Characterization of
    reproducible bugs from \tname.}
  %%   \Fix{Is this up to date? I have seen
  %% lots of activity recently but these numbers remain the
  %% same - Fixed (Abid)}\Fix{Can we add info about whether Python and/or C code causes
  %%     the bug? - Abid: we report how many c,python and cuda native files are buggy in total but not per bug, so currently no}\Fix{Can we add info on whether it is GPU related
  %%     (i.e., only manifests in GPUs)? - Abid: venv-docker is the same
  %%     as cpu-gpu}}
\begin{tabular}{l|rrr}
  \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
  \\ \cmidrule(lr){2-4} \jax{} & 46 & 45-1 & 45-1 \\ \torch{} & 37 &
  18-19 & 21-16 \\ \tf{} & 24 & 23-1 & 24-0 \\ \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 86-21& 90-17
  \\ \bottomrule
\end{tabular}
\end{table}

@@

In this example, the unexpected behavior is a \CodeIn{RuntimeError} thrown by the call to the \CodeIn{fake\_quantize\_per\_channel\_affine} API from \torch. Since the test oracle should pass when the bug is successfully reproduced, the code catches the exception and prints information about it, and upon catching the exception successfully, the test passes. If the bug reproduction fails i.e. the exception is not thrown or a different exception is thrown, the test will fail.

@@

\subsection{Usage}
\label{sec:usage}

@@

The second step runs the \tname's command \CodeIn{run-tool}, which
proceeds in two steps (1) reproduce the bug separately, as done with
command \CodeIn{run-test}, and (2) then update the environment inside
the docker container of the tool to run the tool with the script
provided. The first step is a sanity check to assure that the bug can
indeed be reproduced. For example, the following command runs FreeFuzz
on the enviroment of the bug associated with the issue 117033 from
\torch.

@@

\begin{lstlisting}[language=bash]
...  
[Reproducing the bug]
====== test session starts ======
platform linux -- Python 3.10.0, pytest-8.3.3, pluggy-1.5.0
...
IndexError: list index out of range
====== 1 passed in 1.09s ======
...

[Setting up FreeFuzz]
Updating environment in the container of the testing tool
Successfully copied 16.4kB to freefuzz:/tmp/issue_117033
__pycache__  install_environment.sh  reproduce_bug.sh  requirements.txt  test_issue_117033.py
...

[Running FreeFuzz]
Running the testing tool on the environment of the bug
Testing on  ['torch']
torch.log2
...
torch.nn.MaxUnpool2d
../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [1,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [2,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
...
\end{lstlisting}

@@

@@

We anticipate two major use cases for \tname: (1) \textbf{evaluation
  of testing techniques} and (2) \textbf{evaluation of repair
  techniques}. Dozens of API- and model-level testing techniques have
been proposed in the literature recently and it is imperative to
evaluate them using a standard benchmark. \tname\ provides such
benchmark. Considering repair, as testing techniques mature it becomes
important to identify candidate repairs that can be recommended to
developers when reporting issues in bug trackers. With \tname\ it is
possible to identify if the problem has been resolved.

\section{Related Work}

Several bug datasets have been proposed in literature for general
software. Some popular examples includes software-artifact
infrastructure repository (SIR)~\cite{do2005supporting} which was one
of the bug datasets containing 81 artificial faults in projects across
multiple languages, Defects4J~\cite{just2014defects4j} which includes
357 real bugs across five large real-world Java projects,
BugsInPy~\cite{widyasari2020bugsinpy} containing 493 real bugs from 17
real-world Python programs, and BugsJS~\cite{vancsics2020relationship}
containing 453 bugs across 10 Javascript projects.
%
Google's FuzzBench~\cite{metzman2021fuzzbench} provides an evaluation platform
for comparing general purpose fuzzers. Magma~\cite{hazimeh2020magma} is another
fuzzing benchmark built by \emph{front-porting} real bugs in latest version of
projects. In contrast to these general purpose benchmarks, \tname includes
reproducible bugs for Deep Learning libraries like PyTorch and TensorFlow, and
allows systematic benchmarking for DLL fuzzers.

@@

\section{Conclusion and Future Work}
Deep Learning (DL) Libraries (e.g., \torch) provide the basic blocks
for creating AI-enabled applications, which are becoming very
popular. Several testing techniques have been proposed in the
literature to find bugs on these libraries. Unfortunately, the lack of
a dataset of reproducible bugs in those libraries poses a barrier to
a proper evaluation of these techniques. \tname{} fills the gaps by

\balance
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

@@

Section~\ref{sec:usage} demonstrates usage of \tname. The reader can
also follow the steps in the README.md file on our GitHub repository.
